\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-27 OaklandSubmission/impl.tex
partitioning

We use an off-the-shelf solver
(SeaHorn~\cite{seahorn}) to bound check the array indices
($\Gamma\vDash e < n$
in ({\sc {T-Read}}) and ({\sc{T-Write}})),
Figure~\ref{fig:compile}). We take the \tool source program and
translate it as an input to the solver. The solver takes less
than a minute on our largest benchmark to verify that all the array
accesses are in-bounds.

@@

The compilation rules of Figure~\ref{fig:compile} can introduce
repeated coercions from arithmetic to
boolean and vice versa.
The \tool implementation performs  the standard ``common subexpression elimination"
optimization to reduce these coercions.
On each coercion, \tool memorizes the pair of arithmetic
share and boolean share involved in the coercion. 
\tool invalidates such pairs when the variables corresponding to the
shares are overwritten by assignments. 
In subsequent coercions, \tool  reuses valid pairs (if available)
instead of inserting code to recompute them afresh.

>>>>

We use an off-the-shelf solver
(SeaHorn~\cite{seahorn}) to bound check the array indices
($P\vDash e < n$
in ({\sc {T-Read}}) and ({\sc{T-Write}})),
Figure~\ref{fig:compile}). We take the \tool source program and
translate it as an input to the solver. The solver takes less
than a minute on our largest benchmark to verify that all the array
accesses are in-bounds.

@@

The compilation rules of Figure~\ref{fig:compile} can introduce
repeated coercions from arithmetic to
boolean and vice versa.
The \tool implementation performs  the standard ``common subexpression elimination"
optimization~\cite{dragonbook} to reduce these coercions.
On each coercion, \tool memorizes the pair of arithmetic
share and boolean share involved in the coercion. 
\tool invalidates such pairs when the variables corresponding to the
shares are overwritten by assignments. 
In subsequent coercions, \tool  reuses valid pairs (if available)
instead of inserting code to recompute them afresh.

### 2017-10-27 OaklandSubmission/pipe.tex
partitioning

\section{Pipelining}
\label{sec:pipe}
\nc{Started high level description. Can go deeper and correct notation as we proceed.}
We now describe our technique of ``pipelining'' that allows us to compile and execute large programs that would otherwise have not fit in memory (due to the large size of the circuit generated by ABY). We do this securely in a manner such that the underlying backend (such as ABY in this case) does not have to modified in anyway and hence our technique is also compatible with any backend. In more detail, let $P$ be a program in our source language that gets compiled to $P'$ in our target language. In many cases, the ABY circuit generated for $P'$ is very large and cannot fit in memory (in fact, there is an upper limit of $2^{32}$ for the circuit size in ABY and for many natural programs, this upper limit is easily crossed). Without pipelining, we would be unable to compile and execute such a program $P$. In order to overcome this size limit, we do the following: we split the program $P$ into a sequence of smaller programs $Q_1||Q_2||\cdots||Q_k$ (that will be appropriately defined). We compile and execute each $Q_i$ separately, feeding the outputs of one program as state information to the next program. Of course, we have to be careful how we do this so as to not compromise the security of the protocol. More details follow.

Let $P$ be a program that takes as (secret) inputs $x$ and $y$ and produces output $z$ to both parties. Let $P_1||P_2||\cdots||P_k$ be a sequence of programs defined such that the following holds. Define $s_0 = \bot$ (the public empty state). For all $1\leq i\leq k-1$, $P_i$ takes as input $x, y$ and $s_{i-1}$ to produce state information $s_i$. Finally, $P_k$ takes as input $x,y$ and $s_{k-1}$ to produce output $z$. Every program $P_i$ ($1\leq i\leq k$) will be required to be ``sufficiently'' small (as described later) and this will enable our pipelining technique. It is easy to see that any program $P$ can be decomposed as illustrated above into such $P_1||P_2||\cdots||P_k$. Now, if one were to compile $P_i$ into $P'_i$, and execute $P'_i$, the parties can execute $P'_1||P'_2||\cdots||P'_k$ sequentially to obtain $s_1,\cdots,s_{k-1},$ and finally output $z$. At the $i^{\textrm{\tiny{th}}}$ step, the parties would only need to store information proportional to $x,y,s_i$ and $P'_i$ (which will all be much smaller than $P'$). However, if we were to execute the programs as outlined above, it would enable the parties to learn $s_i$ (for all $1\leq i\leq k-1$), which would completely break the security of the protocol.

To overcome this problem, we define a sequence of new programs $Q_i$ ($1\leq i\leq k$) as follows. Once again, define $s_0 = \bot$. Let all $s_i$ be values in some additive ring $(\mathbb{Z},+)$ (in the ABY implementation this ring would simply be the additive ring $(\mathbb{Z}_{2^{32}},+)$ i.e., the additive ring of integers modulo $2^{32}$). This is without loss of generality true (we will also for simplicity assume that each $s_i$ is a single element in the ring, but this restriction can also be easily removed). Let $r_1,\cdots,r_{k-1}$ be a sequence of random values sampled from the same ring $(\mathbb{Z},+)$ by Party A (in our implementation, all $r_i$ values can be generated using a pseudorandom function $F$). Let $Q_1$ be the program that takes as input $x,y, r_1$ (and empty state $s_0$), runs $P_1$ (as defined above) to get $s_1$ and then produces output $o_1 = s_1 + r_1$ {\em only to} Party B\footnote{While the description of our protocol here assumes that the underlying backend supports only one party receiving output, this is only a simplifying assumption, and we can easily modify our protocol in the case where both parties must receive the same output. To do so, we let $Q_1$ output $o_1 = s_1+r_1+t_1$ (where $t_1$ is random and chosen by Party B) and have both parties learn this. We can then appropriately modify the remaining steps as well.}. The output of $Q_1$ for Party A in Step 1 is defined to be $r_1$. Now, every $Q_i$ ($2\leq i\leq k-1$) takes as input $x,y,r_{i-1},o_{i-1},r_i$, runs $P_i$ on inputs $x,y$ and state $o_{i-1}-r_{i-1}$ to get $s_i$ (where $-$ denotes subtraction in the ring $(\mathbb{Z},+)$) and then produces $s_i+r_i$ as output only to Party B. Again, Party A's output for $P_i$ is defined to be $r_i$. $Q_k$ takes as input $x,y,r_{k-1},o_{k-1}$, runs $P_k$ on inputs $x,y$ and state $o_{k-1}-r_{k-1}$ and outputs $z$ to both parties.

Our compiler, given $P$, will first split $P$ into $P_1||P_2||\cdots||P_k$ with the guarantee that the ABY circuits generated for every $Q_i$ defined above is small enough to fit into memory. It will then compile and execute the $k$ programs $Q_1||Q_2||\cdots||Q_k$ sequentially (freeing up memory usage after every execution) to produce final output $z$ to both parties.

>>>>

\section{Secure code partitioning}
\label{sec:pipe}

We  describe ``secure code partitioning'' that allows us to execute {\it large} programs, i.e., programs with a large number of operations.
In more detail, let $P$ be a program in our source language that generates a circuit $\crct$. For a large enough $P$, the circuit $\crct$  can be larger than the memory size\footnote{In fact, there is an upper limit of $2^{32}-1$ gates for the circuit size in ABY but for most machines the memory limit is hit first} and fail to execute. Partitioning enables us to
execute such programs via a source to source transformation that is oblivious to the underlying \mpc backend. Partitioning decomposes the program $P$ into a sequence of smaller \tool programs $Q_1||Q_2||\cdots||Q_k$ (defined below). We compile and execute each $Q_i$ sequentially, feeding the outputs of $Q_i$ as state information to $Q_{i+1}$. We prove that partioning is correct ($P$ and $Q_1||Q_2||\cdots||Q_k$ compute the same functionality) and secure (execution of $Q_1||Q_2||\cdots||Q_k$ does not reveal any more information than $P$). More details follow.

Let $P$ be a program that takes (secret) inputs $x$ and $y$ and produces an output $z$ to both parties (Alice and Bob). Let $P_1||P_2||\cdots||P_k$ be a sequence of programs such that the following holds: Define $s_0 = \bot$ (the public empty state). For all $1\leq i\leq k-1$, $P_i$ takes inputs $x, y$ and $s_{i-1}$ and outputs  state information $s_i$. Finally, $P_k$ takes inputs $x,y$ and $s_{k-1}$ to  output $z$. Each program $P_i$ ($1\leq i\leq k$) is required to be ``sufficiently'' small (as described later). It is possible to decompose any program $P$  into such $P_1||P_2||\cdots||P_k$. If \tool generates circuit $\crct_i$ from $P_i$, the parties can execute $\crct_1||\crct_2||\cdots||\crct_k$ sequentially (in a distributed setting)  to obtain $s_1,\cdots,s_{k-1},$ and finally output $z$. At the $i^{\textrm{\tiny{th}}}$ step, the parties only need to store information proportional to $x,y,s_{i-1}$ and $\crct_i$ (which is much smaller than $\crct$). However, this execution enables the parties to learn $s_i$ (for all $1\leq i\leq k-1$), which completely breaks the security.

To overcome this problem, we define a sequence of new programs $Q_i$ ($1\leq i\leq k$) as follows. Once again, define $s_0 = \bot$. Without loss of generality, let all $s_i$ be values in some additive ring $(\mathbb{Z},+)$ (e.g., the additive ring $(\mathbb{Z}_{2^{64}},+)$ i.e., the additive ring of integers modulo $2^{64}$). 
Let $r_1,\cdots,r_{k-1}$ be a sequence of random values sampled from the same ring $(\mathbb{Z},+)$ by Alice (in our implementation, all $r_i$ values are generated by a pseudorandom function). Let $Q_1$ be the program that takes as inputs $x,y, r_1$ (and empty state $s_0$), runs $P_1$ (as defined above) to get $s_1$ and then outputs $o_1 = s_1 + r_1$ {\em only to} Bob\footnote{While the description of our protocol here assumes that the underlying backend supports only one party receiving output, this is only a simplifying assumption, and we can easily modify our protocol in the case where both parties must receive the same output. To do so, we let $Q_1$ output $o_1 = s_1+r_1+t_1$ (where $t_1$ is random and chosen by Bob) and have both parties learn this. We can then appropriately modify the remaining steps as well.}. Alice's output from $Q_1$ is $r_1$. Next, every $Q_i$ ($2\leq i\leq k-1$) takes as inputs $x,y,r_{i-1},o_{i-1},r_i$, runs $P_i$ on inputs $x,y$ and state $o_{i-1}-r_{i-1}$ (where $-$ denotes subtraction in the ring $(\mathbb{Z},+)$) and then outputs $s_i+r_i$ only to Bob. Again, Alice's output from $P_i$ is $r_i$. The last program $Q_k$ takes inputs $x,y,r_{k-1},o_{k-1}$, runs $P_k$ on inputs $x,y$ and state $o_{k-1}-r_{k-1}$ and outputs $z$ to both parties.

Given $P$, partitioning first decomposes $P$ into $P_1||P_2||\cdots||P_k$ with the guarantee that the circuits generated for every $Q_i$ defined above are small enough to fit in the machine memory. We then compile and execute the $k$ programs $Q_1||Q_2||\cdots||Q_k$ sequentially (freeing up memory usage after  execution of each $Q_i$) to finally output $z$ to both parties.

\begin{theorem}[Correctness and security of partitioning]
Let $P$ be a program in our source language with output $z$, that is decomposed into programs $Q_1||Q_2||\cdots ||Q_k$ (as defined in the partioning procedure above) and compiled into the protocol $\prot_1||\prot_2\cdots ||\prot_k$ that outputs $r_1||r_2||\cdots||z$ (to Alice) and $o_1||o_2||\cdots||z$ (to Bob), then $\prot$ securely realizes $P$.  
\end{theorem}

\noindent {\em Proof.} From Theorem \ref{theorem:security}, it follows that $\prot_i$ securely realizes $Q_i$ for every $1\leq i\leq k$. Hence, we know that the only information learnt by Alice is $r_1||r_2||\cdots||r_{k-1}||z$ and by Bob is $o_1||o_2||\cdots||o_{k-1}||z$. Since $r_i$ and $o_i$ ($1\leq i\leq k-1$) are individually uniformly random (in $(\mathbb{Z},+)$, the proof follows.

Our current implementation of secure code partitioning requires a manual step.
In particular, the developer needs to decompose the large program $P$ into 
the sequence of small programs $P_1||\ldots||P_k$ manually.
Then \tool generates $Q_1||\ldots||Q_k$ automatically.
Automating this decomposition step requires an analysis that can 
statically estimate the resource usage of a \tool program and we leave the construction of such
an analysis as future work.
